Fluent statistical computing interfaces for biological data analysis

### 2020-08-03 Rmd/04-intron.Rmd
fix typos found in #10

The gene annotation files were
obtained as GFF files from RefSeq and used that to construct the exonic
and intronic parts of each gene as _GRanges_ object using **superintronic**. 
We further filtered genes that had a single exon or genes that were overlapping
others in the annotation and that were not on the main contigs of the reference genome (i.e. excluding mitochondria) to simplify our analysis and reduce any coverage ambiguity. This left 18,270 genes available for 
computing data descriptors on in order to detecting IR-like coverage traces. Across each combination of genotype and line, we first $log_2$ transformed the coverage score with an offset of one, and then intersected the coverage _GRanges_ with exonic and intronic features of each gene. For each gene,
the weighted mean and standard deviation of the log-transformed coverage score were computed over all intron and exon parts within the groupings of 
genotype and line. We also computed the bases above descriptor for intron
features. It refers to the total number of bases within an intron that has a score above the overall average exon coverage score. The scatter plot 
matrix view of these descriptors is shown in figure \@ref(fig:si-splom)
for a single biological group in the experiment. Using these views and
by summarising over the data descriptors, we came up with thresholds
for finding genes that have IR-like traces within each biological group.

@@

We have shown how to coverage can be represented in the tidy data framework
and integrated with experimental metadata and reference annotations. This
framework allowed us to build data descriptions that are simple aggregations of
various aspects of genomic features over factors within a designed experiment
and link those descriptions to their underlying coverage traces.

>>>>

The gene annotation files were
obtained as GFF files from RefSeq and used to construct the exonic
and intronic parts of each gene as _GRanges_ object using **superintronic**. 
We further filtered genes that had a single exon or genes that were overlapping
others in the annotation and that were not on the main contigs of the reference genome (i.e. excluding mitochondria) to simplify our analysis and reduce any coverage ambiguity. This left 18,270 genes available for 
computing data descriptors on in order to detecting IR-like coverage traces. Across each combination of genotype and line, we first $\log_2$ transformed the coverage score with an offset of one, and then intersected the coverage _GRanges_ with exonic and intronic features of each gene. For each gene,
the mean and standard deviation of the log-transformed coverage score weighted by the number of bases covered were computed over all intron and exon parts within the groupings of 
genotype and line. We also computed the bases above descriptor for intron
features. It refers to the total number of bases within an intron that has a score above the overall average exon coverage score. The scatter plot 
matrix view of these descriptors is shown in figure \@ref(fig:si-splom)
for a single biological group in the experiment. Using these views and
by summarising over the data descriptors, we came up with thresholds
for finding genes that have IR-like traces within each biological group.

@@

We have shown how coverage can be represented in the tidy data framework
and integrated with experimental metadata and reference annotations. This
framework allowed us to build data descriptions that are simple aggregations of
various aspects of genomic features over factors within a designed experiment
and link those descriptions to their underlying coverage traces.
